---
name: Tim Jockusch
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: MS Data Science and Analytics, BS Statistics
position: Data Science and Analytics student
address: Grand Rapids, Michigan
#profilepic: "files/Profpic.jpg"
phone: 616 617 5032
email: Tim.Jockusch@gmail.com
github: Jockusct
headcolor: "990000"
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
tinytex:::install_prebuilt()
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```


# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "Master of Science in Data Science and Analytics", "Grand Valley State University", "Grand Rapids, Michigan", "Expected Graduation: December 2022", "Utilizing R, SQL, SAS, and Python to solve real world data problems.",
  "Bachelor of Science in Statistics", "Grand Valley State University", "Grand Rapids, Michigan", "Aug 2016 - Apr 2020", "Math and Stats club",
    "Bachelor of Science in Statistics", "Grand Valley State University", "Grand Rapids, Michigan", "Aug 2016 - Apr 2020", "Deans List: Fall 2017, Winter 2019, Winter 2020 "
) %>% 
  detailed_entries(what=degree, when=dates, with=uni, where=loc, why=details)
```

# Experience

```{r Experience}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Customer Service Representative", "Enterprise-Rent-A-Car", "Grand Rapids, Michigan", "May 2017- August 2019", "Handled up to 300+ customers a day, with duties including communicating detailed contracts, rental policies, and procedures.",
  "Customer Service Representative", "Enterprise-Rent-A-Car", "Grand Rapids, Michigan", "May 2017- August 2019", "Used selling techniques to maximize profit for the company.",
    "Customer Service Representative", "Enterprise-Rent-A-Car", "Grand Rapids, Michigan", "May 2017- August 2019","Helped Enterprise achieve increasing customer service scores each month.",
  "Student Statistical Consultant","Grand Valley State University", "Allendale, Michigan","January 2019- April 2019","Analyzed the impact of Activity-based learning on students' attitudes towards Mathematics.",
    "Student Statistical Consultant","Grand Valley State University", "Allendale, Michigan","January 2019- April 2019","Used excel, SAS, SPSS, and Tableau to analyze Likert scale survey data.",
    "Student Statistical Consultant","Grand Valley State University", "Allendale, Michigan","January 2019- April 2019","Analyzed and compared multiple one-tailed paired sample t-tests and data trends.",
     "Student Statistical Consultant","Grand Valley State University", "Allendale, Michigan","January 2019- April 2019","Presented results at Student Scholars Day GVSU."
) %>% 
  detailed_entries(what=role, when=dates, with=company, where=loc, why=details)
```

# Skills

```{r skills}
tribble(
  ~ area, ~ skill,
 "Programming Langauges","R, SAS, SQL, Javascript, Python",
 "Microsoft Office", "Excel, Word, Powerpoint",
 "Version Control" , "Git",
 "Data Analysis", "Data Cleaning, Visualisation, Modeling, Machine Learning, Web Scraping ",
    "Strong analytical and problem-solving skills", "",
    "Team-Player with excellent communication skills", "",
    "Strong desire to learn", ""
) %>% 
  detailed_entries(with=area,what=skill)
```


# Languages 

```{r language}
tribble(
  ~ language, ~ fluent,
"German", "Fluent"
) %>% 
  detailed_entries(with=language,what=fluent)
```

# Certifications 

```{r certifications}
tribble(
  ~ title, ~ source, ~ date,
"Cleaning Data In R with Tidyverse and Data.table", "Udemy", "Programming",
  "Data Science and Machine Learning Bootcamp with R", "Udemy", "Programming",
   "Master SQL for Data Science", "Udemy", "Database Querying",
  "Data Analysis with Pandas and Python", "Udemy", "Programming",
  "Python For Data Science and Machine Learning Bootcamp", "Udemy", "Programming",
  "SAS Programming BASE Certification course", "Udemy", "Programming",
  "SQL for Data Analysis", "Udemy", "Database Querying",
  "The Complete SQL Bootcamp 2020" , "Udemy", "Database Querying",
  "R Programming: Advanced Analytics in R For Data Science", "Udemy", "Programming",
  "Microsoft Excel - Data Anlaysis With Excel Pivot Tables", "Udemy", "Microsoft Office"
) %>% 
  detailed_entries(why=title,with=date,when=source)